Improving the communication and transparency of stock assessment using interactive

### 2019-01-09 analysis/paper/manuscript.Rmd
Make a panel figure for NCAM dashboard screenshots

TODO:
- Take screenshots of the dashboard for static figures for the paper (use webshot?)
- Remember to add reference to the supplement that will ultimately include the NCAM_dashboard.html

>>>>

The NCAM dashboard contains a series of tabs, the first of which provides a series of tarse point-form background on the model (Figure \@ref(fig:background)).

TODO: Aggregate screenshots into one a, b, c, etc. image.

```{r background, echo = FALSE, fig.cap = "- Screenshots of NCAM dashboard."}
knitr::include_graphics("figures/NCAM_dashboard_background_tab.png")
```

...useful format for meetings because a self-contained html can be produced for participants to independently scrutinize. This html has been included as a supplement (Supplement 2)...
